### 2014-08-12 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edit to timeline (related to r551)

\begin{table}
\centering
\captionof{table}{Fire incident and simulation event timeline}\label{tab:firesim}
\begin{tabular}{ccl}
\toprule[1.5pt]
Incident Time  &  Simulation Time  &  Fire Behavior / Fireground Operation  \\
{[hh:mm:ss]}   &  {[s]}            &                                        \\
\midrule
\multirow{2}{*}{17:15:00} &    & \multirow{2}{*}{\parbox{9cm} {Fire is reported with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
         & & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
\multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{9cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}} \\
         & & \\[.25cm]
\multirow{3}{*} {} &  \multirow{3}{*} {0} &  \multirow{3}{*}{\parbox{8cm} {FDS simulation starts. Attic fire ignites. Initial ventilation through rear of structure. Front door open.}} \\
         & & \\[0.25cm]
         & & \\[0.25cm]
\multirow{3}{*}{17:20:00} & \multirow{3}{*}{40}  & \multirow{3}{*}{\parbox{9cm} {Attic windows break - heavy smoke out of front attic window and heavy smoke and fire out of rear. Rear porch ignites in model.}} \\
         & & \\[.25cm]
         & & \\[.25cm]  
\multirow{2}{*}{}  & \multirow{2}{*}{45} & \multirow{2}{*}{\parbox{8cm}{Ventilation through wall penetration on rear of structure.}} \\
          & & \\[.25cm] 
\multirow{2}{*}{}  & \multirow{2}{*}{55}  & \multirow{2}{*}{\parbox{8cm}{Ventilation through wall penetration on left side of structure.}} \\ 
          & & \\[.25cm] 
\multirow{2}{*}{17:21:00} & \multirow{2}{*}{100} & \multirow{2}{*}{\parbox{8cm}{E123 captain and firefighter on second floor with 1\sfrac{3}{4}-inch hoseline.}} \\
         &  & \\[.25cm]
\multirow{2}{*}{17:21:30} & \multirow{2}{*}{130} &  \multirow{2}{*}{\parbox{8cm}{First floor exterior porch door opened. Porch fire ignites in FDS model.}} \\
        &  & \\[.25cm]
        & 135 & Ventilation through left side of structure. \\[.25cm] 
        & 160 & Top of interior door fails in FDS model. \\[.25cm] 
\multirow{3}{*}{17:23:00}    & \multirow{3}{*}{220} & \multirow{3}{*}{\parbox{8cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}} \\
         & & \\[.25cm]
         & & \\[.25cm]  
17:24:00    &   & Water applied to attic from the rear exterior position. \\[.25cm]
17:25:00    &   & SQ5 makes entry through front of structure. \\[.25cm]
\multirow{2}{*}{17:27:00}    & \multirow{2}{*}{300}  & \multirow{2}{*}{\parbox{8cm} {After hearing a Mayday call from SQ5, IC calls a Mayday. Simulation ends.}}\\
         & &  \\[.25cm]
17:29:00    &   & E123 captain carried out of structure. \\
\bottomrule[1.25pt]
\end{tabular}\par
\footnotesize
For specific information regarding ventilation areas used in the FDS model, refer to Table~\ref{tab:vents}.
\normalsize
\end{table}

>>>>

\begin{table}
\centering
\captionof{table}{Fire incident and simulation event timeline}\label{tab:firesim}
\begin{tabular}{ccl}
\toprule[1.5pt]
Incident Time  &  Simulation Time  &  Fire Behavior / Fireground Operation  \\
{[hh:mm:ss]}   &  {[s]}            &                                        \\
\midrule
\multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{9cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}} \\
         & & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
\multirow{2}{*}{17:17:00} &    & \multirow{2}{*}{\parbox{9cm} {On-scene report of a working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
         & & \\[.25cm]
\multirow{3}{*} {} &  \multirow{3}{*} {0} &  \multirow{3}{*}{\parbox{8cm} {FDS simulation starts. Attic fire ignites. Initial ventilation through rear of structure. Front door open.}} \\
         & & \\[0.25cm]
         & & \\[0.25cm]
\multirow{3}{*}{17:20:00} & \multirow{3}{*}{40}  & \multirow{3}{*}{\parbox{9cm} {Attic windows break - heavy smoke out of front attic window and heavy smoke and fire out of rear. Rear porch ignites in model.}} \\
         & & \\[.25cm]
         & & \\[.25cm]  
\multirow{2}{*}{}  & \multirow{2}{*}{45} & \multirow{2}{*}{\parbox{8cm}{Ventilation through wall penetration on rear of structure.}} \\
          & & \\[.25cm] 
\multirow{2}{*}{}  & \multirow{2}{*}{55}  & \multirow{2}{*}{\parbox{8cm}{Ventilation through wall penetration on left side of structure.}} \\ 
          & & \\[.25cm] 
\multirow{2}{*}{17:21:00} & \multirow{2}{*}{100} & \multirow{2}{*}{\parbox{8cm}{E123 captain and firefighter on second floor with 1\sfrac{3}{4}-inch hoseline.}} \\
         &  & \\[.25cm]
\multirow{2}{*}{17:21:30} & \multirow{2}{*}{130} &  \multirow{2}{*}{\parbox{8cm}{First floor exterior porch door opened. Porch fire ignites in FDS model.}} \\
        &  & \\[.25cm]
        & 135 & Ventilation through left side of structure. \\[.25cm] 
        & 160 & Top of interior door fails in FDS model. \\[.25cm] 
\multirow{3}{*}{17:23:00}    & \multirow{3}{*}{220} & \multirow{3}{*}{\parbox{8cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}} \\
         & & \\[.25cm]
         & & \\[.25cm]  
17:24:00    &   & Water applied to attic from the rear exterior position. \\[.25cm]
17:25:00    &   & SQ5 makes entry through front of structure. \\[.25cm]
\multirow{2}{*}{17:27:00}    & \multirow{2}{*}{300}  & \multirow{2}{*}{\parbox{8cm} {After hearing a Mayday call from SQ5, IC calls a Mayday. Simulation ends.}}\\
         & &  \\[.25cm]
17:29:00    &   & E123 captain carried out of structure. \\
\bottomrule[1.25pt]
\end{tabular}\par
\footnotesize
For specific information regarding ventilation areas used in the FDS model, refer to Table~\ref{tab:vents}.
\normalsize
\end{table}
